Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
reflow, tidy
conclusion ps

# Discussion
<!-- 
outline

1. TODO intro

2. social scale. our results. possible extensions with HMM. observational of dif behaviours

3. habitat+social, implicit -> explicit, our results.

4. movement, 1 sent biolog

5. seasonality, time windows

6. number obs

@@

<!-- (this was the) conclusion -->
Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks are scale-dependent, and (2) 
the use of multilayer networks is useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability.

Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. <!-- rm tech-->In addition, recent technological
advances have lead to increased data complexity and resolution. Remotely sensed
imagery collected by modern satellites provide, for example, 10 m spatial
resolution optical imagery at a temporal revisit period of five days at the
equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
at a higher temporal resolution [@B_rger_2016]. <!-- rm tech-->Given<!-- the increased.. 
complex + higher resolution + remotely sensed--> this increased
availability of complex data, it is important to consider using a broad
continuum of scales to fully capture ecological processes, carefully select and
combine sources of data with different temporal and spatial scales, and
establish a clear link between scales of observation and meaningful biology.

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks which incorporated high resolution GPS telemetry data and spatial land cover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has <!-- edit-->traditionally been done in
ethology. We highlight ways in which scale ought to be considered for both
observed and remotely-sensed data when building social networks. GPS telemetry 
data provides a link between large scale landscape properties and
fine scale social interactions as animal movement occurs across the landscape,
and when taken into account with multiple individuals<!-- edit--> can indicate association
patterns. Thus, a layer incorporating relocation data could be a great boon
linking spatial and social layer in multilayer networks.
<!-- JWT: It think we need an ending thought or punch or something, not end it on a question. -->
<!-- (this was the) conclusion -->

>>>>

# Discussion
<!--
1. intro

@@

<!-- (this was the) conclusion -->

Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. Recent technological advances in
remotely sensed imagery [@Drusch_2012] and animal tracking devices
[@B_rger_2016; @Wikelski_2007] have increased the availability of complex, high
resolution data. We highlight ways in which scale should be considered when
building social networks from both observed and remotely-sensed data. It is
important to consider a broad continuum of scales to fully capture ecological
processes, carefully select and combine sources of data with different temporal
and spatial scales, and establish a clear link between scales of observation and
meaningful biology.

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the novel analyses in varying social, spatial,
and temporal scale within a multilayer framework. We show that (1) multilayer
social networks are scale-dependent, and (2) the use of multilayer networks is
useful for identifying habitat or season-specific social processes. Our analysis
of caribou multilayer networks incorporating high resolution GPS telemetry data
and spatial land cover data is grounded in the context of observed animal social
networks, as the scales we chose to explore, e.g., number of observations and
sociality across space and time, are ones that have also traditionally been done
in ethology.

<!-- TODO: round it out -->

<!-- (this was the) conclusion -->
